---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
Load packages for data analysis:
```{r}
library(ggplot2)
library(dplyr)
```

Unzip the zip file
```{r}
unzip(zipfile = "activity.zip")
```

Read the data into R
```{r}
steps_data <- read.csv("activity.csv")
```

Create dataset without missing values
```{r}
steps_data_complete <- na.omit(steps_data)
```

## What is mean total number of steps taken per day?
Create a new data frame with the sum of the steps for each date and name the 
columns appropriately
```{r}
steps_per_day <- with(steps_data_complete, aggregate(steps, by = list(date),
                                                     sum))
names(steps_per_day) <- c("Date", "Steps")
```

Calculate the average number of steps per day
```{r}
avg_steps <- mean(steps_per_day$Steps)
```

Caluculate the median number of steps per day
```{r}
median_steps <- median(steps_per_day$Steps)
```

The average number of steps per day is `r avg_steps` and the median number of
steps per day is `r median_steps`.

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
